---
title: "unit15-final"
author: "Omid Mehrpour"
date: "11/29/2021"
output: html_document
---

First load the required libraries
```{r, message=FALSE, warning=FALSE, out.width="100%"}
rm(list = ls())

library(vtable)
library(scales)
library(corrplot)
library(nortest)
library(randomForest)
library(foreign)
library(GGally)
library(haven)
library(magrittr)
library(data.table)
library(dplyr)
library(plyr)
library(nycflights13)
library(tidyverse)
library(datasets)
library(readxl)
library(maps)
library(plotly)
library(DT)
library(tidytext)
library(plyr)
library(factoextra)
library(readxl)
library(plotly)
library(naivebayes)
library(caTools)
library(devtools)
library(ggcorrplot)
library(usethis)
library(fastDummies)
library(recipes)
library(caretEnsemble)
library(readr)
library("gplots")
library(dominanceanalysis)
library(caTools)
library(randomForest) 
library(xgboost) 
library(data.table)
library(plyr)
library(nycflights13)
library(datasets)
library(readxl)
library(magrittr)
library(maps)
library(plotly)
library(plyr)
library(GGally)
library(readxl)
library(plotly)
library(graphics)
library(e1071)
library(caTools)
library(ggplot2)
library(caret)
library(caretEnsemble)
library(psych)
library(GGally)
library(rpart)
library(randomForest)
library(readr)
library(vtable)
library(scales)
library(gridExtra)
library(corrplot)
library(nortest)
library(class)
library(randomForest)
library(foreign)
library(foreign)
library(GGally)
library(data.table)
library(plyr)
library(ggmap)
library(nycflights13)
library(datasets)
library(readxl)
library(DataExplorer)
library(maps)
library(plotly)
library(plyr)
library(GGally)
library(readxl)
library(plotly)
library(mice)
library(caTools)
library(lattice)
library(ggcorrplot)
library(usethis)
library(fastDummies)
library(recipes)
library(GGally)
library(caretEnsemble)
library(Amelia)
library(GGally)
library(randomForest)
library(readr)
library(aod)
library("gplots")
library(caret)
library(dominanceanalysis)
library(caTools)
library(randomForest) # for fitting RFs
library(skimr)
library(GGally)
library(plotly)
library(viridis)
library(caret)
library(randomForest)
library(rpart.plot)
library(corrgram)
library(h2o)
library(ggthemes)
library(treemap)
library(treemapify)
library(repr)
library(cowplot)
library(magrittr)
library(ggpubr)
library(RColorBrewer)
library(plotrix)
library(ggrepel)
library(forcats)
library(reshape2)
library(caTools)
library(tree)
library(rattle)
library(foreign)
library(haven)
library(ggplot2)
library(foreign)
library(ggplot2)
library(GGally)
library(haven)
library(magrittr)
library(data.table)
library(dplyr)
library(plyr)
library(dplyr)
library(factoextra)
library(ggplot2)
library(ggmap)
library(nycflights13)
library(tidyverse)
library(datasets)
library(readxl)
library(tidyverse) 
library(magrittr)
library(DataExplorer)
library(maps)
library(plotly)
library(DT)
library(tidytext)
library(plyr)
library(gridExtra)
library(factoextra)
library(GGally)
library(readxl)
library(tidyverse) 
library(magrittr)
library(DataExplorer)
library(maps)
library(plotly)
library(DT)
library(tidytext)
library(gridExtra)
library(factoextra)
library(GGally)
library(gridExtra)
library(graphics)
library(mice)
library(naivebayes)
library(e1071)
library(caTools)
library(lattice)
library(ggplot2)
library(tidyverse)
library(caret)
library(caretEnsemble)
library(psych)
library(Amelia)
library(mice)
library(GGally)
library(rpart)
library(randomForest)
library(scales)
library(readr)
options(repr.plot.width=8, repr.plot.height=6)
options(warn=-1)

```
Lets import the data sets

```{r, message=FALSE, warning=FALSE, out.width="100%"}
df=read.csv("/Users/owner/Desktop/homework/unit14,15(case sudy)/CaseStudy2-data.csv")


cs2.NoAttrition =  read.csv("/Users/owner/Desktop/homework/unit14,15(case sudy)/Unit%2014%20and%2015%20Case%20Study%202 2/CaseStudy02/CaseStudy2CompSet No Attrition.csv",stringsAsFactors = TRUE)


cs2.NoSalary = read.csv("/Users/owner/Desktop/homework/unit14,15(case sudy)/Unit%2014%20and%2015%20Case%20Study%202 2/CaseStudy02/CaseStudy2CompSet No Salary.csv",stringsAsFactors = TRUE)
```

#visualize the missing data
```{r, message=FALSE, warning=FALSE, out.width="100%"}
sum(is.na(df))
(sum(is.na(df))/prod(dim(df)))*100
```


#================quick look at data and data processesing========
```{r, message=FALSE, warning=FALSE, out.width="100%"}

df %>% group_by(JobRole) %>% summarise(n=n()) %>% arrange(desc(n))

df$Educational_Levels <-  ifelse(df$Education == 1, "Without College D.",
                                 ifelse(df$Education == 2 , "College D.",
                                        ifelse(df$Education == 3, "Bachelors D.",
                                               ifelse(df$Education == 4, "Masters D.", "Phd D."))))

st(df)
```
Define the type of variables

```{r, message=FALSE, warning=FALSE, out.width="100%"}
df$WorkLifeBalance  =  as.factor(df$WorkLifeBalance)
df$JobRole =  as.factor(df$JobRole  )
df$JobInvolvement=as.factor(df$JobInvolvement)
df$JobSatisfaction=as.factor(df$JobSatisfaction)
df$JobLevel=as.factor(df$JobLevel)
df$JobSatisfaction =  as.factor(df$JobSatisfaction)
df$ TrainingTimesLastYear  =  as.factor(df$TrainingTimesLastYear)
df$ PerformanceRating =  as.factor(df$ PerformanceRating)
df$StockOptionLevel =  as.factor(df$StockOptionLevel)
df$RelationshipSatisfaction =  as.factor(df$RelationshipSatisfaction)
df$Education =  as.factor(df$Education)
df$EnvironmentSatisfaction=as.factor(df$EnvironmentSatisfaction)
df$BusinessTravel=as.factor(df$BusinessTravel)
df$JobSatisfaction=as.factor(df$JobSatisfaction)
df$EnvironmentSatisfaction=as.factor(df$EnvironmentSatisfaction)
df$PerformanceRating=as.factor(df$PerformanceRating)
df$TrainingTimesLastYear=as.factor(df$TrainingTimesLastYear)
df$RelationshipSatisfaction=as.factor(df$RelationshipSatisfaction)
df$WorkLifeBalance=as.factor(df$WorkLifeBalance)
df$Attrition <- as.factor(df$Attrition)
table(df$Attrition)


cs2.NoAttrition$WorkLifeBalance  =  as.factor(cs2.NoAttrition$WorkLifeBalance)
cs2.NoAttrition$JobRole =  as.factor(cs2.NoAttrition$JobRole  )
cs2.NoAttrition$JobInvolvement=as.factor(cs2.NoAttrition$JobInvolvement)
cs2.NoAttrition$JobSatisfaction=as.factor(cs2.NoAttrition$JobSatisfaction)
cs2.NoAttrition$JobLevel=as.factor(cs2.NoAttrition$JobLevel)
cs2.NoAttrition$JobSatisfaction =  as.factor(cs2.NoAttrition$JobSatisfaction)
cs2.NoAttrition$ TrainingTimesLastYear  =  as.factor(cs2.NoAttrition$TrainingTimesLastYear)
cs2.NoAttrition$ PerformanceRating =  as.factor(cs2.NoAttrition$ PerformanceRating)
cs2.NoAttrition$StockOptionLevel =  as.factor(cs2.NoAttrition$StockOptionLevel)
cs2.NoAttrition$RelationshipSatisfaction =  as.factor(cs2.NoAttrition$RelationshipSatisfaction)
cs2.NoAttrition$Education =  as.factor(cs2.NoAttrition$Education)
cs2.NoAttrition$EnvironmentSatisfaction=as.factor(cs2.NoAttrition$EnvironmentSatisfaction)
cs2.NoAttrition$BusinessTravel=as.factor(cs2.NoAttrition$BusinessTravel)
cs2.NoAttrition$JobSatisfaction=as.factor(cs2.NoAttrition$JobSatisfaction)
cs2.NoAttrition$EnvironmentSatisfaction=as.factor(cs2.NoAttrition$EnvironmentSatisfaction)
cs2.NoAttrition$PerformanceRating=as.factor(cs2.NoAttrition$PerformanceRating)
cs2.NoAttrition$TrainingTimesLastYear=as.factor(cs2.NoAttrition$TrainingTimesLastYear)
cs2.NoAttrition$RelationshipSatisfaction=as.factor(cs2.NoAttrition$RelationshipSatisfaction)
cs2.NoAttrition$WorkLifeBalance=as.factor(cs2.NoAttrition$WorkLifeBalance)




cs2.NoSalary$WorkLifeBalance  =  as.factor(cs2.NoSalary$WorkLifeBalance)
cs2.NoSalary$JobRole =  as.factor(cs2.NoSalary$JobRole  )
cs2.NoSalary$JobInvolvement=as.factor(cs2.NoSalary$JobInvolvement)
cs2.NoSalary$JobSatisfaction=as.factor(cs2.NoSalary$JobSatisfaction)
cs2.NoSalary$JobLevel=as.factor(cs2.NoSalary$JobLevel)
cs2.NoSalary$JobSatisfaction =  as.factor(cs2.NoSalary$JobSatisfaction)
cs2.NoSalary$ TrainingTimesLastYear  =  as.factor(cs2.NoSalary$TrainingTimesLastYear)
cs2.NoSalary$ PerformanceRating =  as.factor(cs2.NoSalary$ PerformanceRating)
cs2.NoSalary$StockOptionLevel =  as.factor(cs2.NoSalary$StockOptionLevel)
cs2.NoSalary$RelationshipSatisfaction =  as.factor(cs2.NoSalary$RelationshipSatisfaction)
cs2.NoSalary$Education =  as.factor(cs2.NoSalary$Education)
cs2.NoSalary$EnvironmentSatisfaction=as.factor(cs2.NoSalary$EnvironmentSatisfaction)
cs2.NoSalary$BusinessTravel=as.factor(cs2.NoSalary$BusinessTravel)
cs2.NoSalary$JobSatisfaction=as.factor(cs2.NoSalary$JobSatisfaction)
cs2.NoSalary$EnvironmentSatisfaction=as.factor(cs2.NoSalary$EnvironmentSatisfaction)
cs2.NoSalary$PerformanceRating=as.factor(cs2.NoSalary$PerformanceRating)
cs2.NoSalary$TrainingTimesLastYear=as.factor(cs2.NoSalary$TrainingTimesLastYear)
cs2.NoSalary$RelationshipSatisfaction=as.factor(cs2.NoSalary$RelationshipSatisfaction)
cs2.NoSalary$WorkLifeBalance=as.factor(cs2.NoSalary$WorkLifeBalance)
cs2.NoSalary$Attrition <- as.factor(cs2.NoSalary$Attrition)

Attrition.Yes = subset(df, Attrition == "Yes")
Attrition.No = subset(df, Attrition == "No")
```




# Plot data types
```{r, message=FALSE, warning=FALSE, out.width="100%"}

(d1 = as.data.frame(table(sapply(df, class))))
ggplot(d1, aes(x = Var1, y = Freq)) +
  geom_bar(stat = "identity", col = "blue", fill = "lightblue") +
  labs(x = "Type of Class", y = "Frequency", title = "Column type Frequency")+
  theme_bw()

st(df, group = 'Attrition', group.long = TRUE)
```


# Let's have a better understanding about each feature through a correlation plot

```{r, message=FALSE, warning=FALSE, out.width="100%"}
cols = c("#4c86ad", "#f5dfb3")
df %>%
  dplyr::select(Attrition,MonthlyIncome,YearsSinceLastPromotion,YearsWithCurrManager,YearsAtCompany,YearsInCurrentRole,TotalWorkingYears ) %>%
  GGally::ggpairs(
    lower = list(
      continuous = GGally::wrap("points", col = cols[1],alpha=0.6),
      combo = GGally::wrap("box", fill = "white", col ="black")
    ),
    upper = list(
      continuous = GGally::wrap("cor", col = cols[1]),
      combo = GGally::wrap("facetdensity", col = "black")
    ),
    diag = list(
      continuous = GGally::wrap("barDiag", fill = cols[2], col ="black", bins = 18),
      discrete = GGally::wrap("barDiag", fill = cols[2], col ="black"))
  )

cols = c("#4c86ad", "#f5dfb3")
df %>%
  dplyr::select(Attrition,PercentSalaryHike,MonthlyIncome,HourlyRate,MonthlyRate,DistanceFromHome ) %>%
  GGally::ggpairs(
    lower = list(
      continuous = GGally::wrap("points", col = cols[1],alpha=0.6),
      combo = GGally::wrap("box", fill = "white", col ="black")
    ),
    upper = list(
      continuous = GGally::wrap("cor", col = cols[1]),
      combo = GGally::wrap("facetdensity", col = "black")
    ),
    diag = list(
      continuous = GGally::wrap("barDiag", fill = cols[2], col ="black", bins = 18),
      discrete = GGally::wrap("barDiag", fill = cols[2], col ="black"))
  )
```
#EDA of bivariate data
```{r, message=FALSE, warning=FALSE, out.width="100%"}
#Monthly Income by Gender
Income_by_Gender <- ggplot(df, aes(x=Gender, y=MonthlyIncome, color=Gender, fill=Gender)) + geom_boxplot() + 
  scale_fill_manual(values=c("#F5A9F2", "#5882FA")) + scale_color_manual(values=c("#FE2EF7", "#5858FA")) +
  coord_flip() + labs(title="Are there any Gender Disparities in Income?")
Income_by_Gender
```
Plot the relationship between categorical variables with Attrition:

```{r, message=FALSE, warning=FALSE, out.width="100%"}
#-------More graphs to explore the data-----
ggplot(df, aes(OverTime, ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(JobInvolvement, ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(JobSatisfaction, ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(StockOptionLevel, ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(NumCompaniesWorked, ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(JobSatisfaction, ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(JobSatisfaction, ..count..)) + geom_bar(aes(fill = JobRole), position = "dodge")
ggplot(df, aes(WorkLifeBalance , ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(TrainingTimesLastYear  , ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(PerformanceRating  , ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(StockOptionLevel   , ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(RelationshipSatisfaction    , ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(EnvironmentSatisfaction    , ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(Education, ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(BusinessTravel, ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(JobSatisfaction, ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(EnvironmentSatisfaction, ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(NumCompaniesWorked, ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(PerformanceRating, ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(RelationshipSatisfaction, ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(TrainingTimesLastYear, ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(WorkLifeBalance, ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(OverTime, ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(JobInvolvement, ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")

ggplot(df, aes(JobSatisfaction, ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(JobLevel, ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
ggplot(df, aes(OverTime, ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")
```



#distribution of job satisfaction in attrition.
```{r, message=FALSE, warning=FALSE, out.width="100%"}

ggplot(df, aes(JobSatisfaction, ..count..)) + geom_bar(aes(fill = Attrition), position = "dodge")



```



#------------continious variables-------------



#Evaluation the numeric variables in those with and without attrition using boxplot
```{r, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(df, aes(x=Attrition, y=PercentSalaryHike)) +  geom_boxplot(fill='green')
ggplot(df, aes(x=Attrition, y=MonthlyIncome)) +  geom_boxplot(fill='green')
ggplot(df, aes(x=JobRole, y=MonthlyIncome)) +  geom_boxplot(fill='green')
ggplot(df, aes(x=Attrition, y= HourlyRate)) +  geom_boxplot(fill='green')
ggplot(df, aes(x=JobSatisfaction, y= HourlyRate)) +  geom_boxplot(fill='green')
ggplot(df, aes(x=JobSatisfaction, y=MonthlyIncome)) +  geom_boxplot(fill='green')
ggplot(df, aes(x=Attrition, y=DistanceFromHome)) +  geom_boxplot(fill='green')
ggplot(df, aes(x=JobSatisfaction, y=DistanceFromHome)) +  geom_boxplot(fill='green')
ggplot(df, aes(x=Attrition, y=YearsSinceLastPromotion)) +  geom_boxplot(fill='green')
ggplot(df, aes(x=Attrition, y=YearsWithCurrManager)) +  geom_boxplot(fill='green')
ggplot(df, aes(x=Attrition, y=YearsAtCompany)) +  geom_boxplot(fill='green')
ggplot(df, aes(x=Attrition, y=YearsInCurrentRole)) +  geom_boxplot(fill='green')
ggplot(df, aes(x=Attrition, y=TotalWorkingYears)) +  geom_boxplot(fill='green')
```

#Evaluation the numeric variables in those with and without attrition using scatterplot
```{r, message=FALSE, warning=FALSE, out.width="100%"}

ggplot(df,aes(TotalWorkingYears,MonthlyIncome,color=Attrition))+
  geom_point(shape=4,size=2)+
  geom_smooth(method=lm,se=F)

ggplot(df,aes(YearsInCurrentRole,MonthlyIncome,color=Attrition))+
  geom_point(shape=4,size=2)+
  geom_smooth(method=loess,se=F)

ggplot(df,aes(YearsAtCompany,MonthlyIncome,color=Attrition))+
  geom_point(shape=4,size=2)+
  geom_smooth(method=loess,se=F)

ggplot(df,aes(YearsSinceLastPromotion,YearsInCurrentRole,color=Attrition))+
  geom_point(shape=4,size=2)+
  geom_smooth(method=loess,se=F)

ggplot(df,aes(YearsSinceLastPromotion,YearsInCurrentRole,color=Attrition))+
  geom_point(shape=4,size=2)+
  geom_smooth(method=loess,se=F)


ggplot(df,aes(TotalWorkingYears,YearsSinceLastPromotion,color=Attrition))+
  geom_point(shape=4,size=2)+
  geom_smooth(method=loess,se=F)
```

Evaluation of monthly income using histogram

```{r, message=FALSE, warning=FALSE, out.width="100%"}
### 1. Monthly Income Variable
ggplot(df, aes(x = MonthlyIncome)) + 
  geom_histogram(aes(y = stat(density)), col = "blue", fill = "gold") + 
  geom_density(col = "red", size = 1) + 
  labs(x = "Monthly Income (Salary)",y = " ",
       title = "Histogram for Monthly Income") +
  theme_bw()

range(df$MonthlyIncome)
# Monthly Income variable is not normally distributed and variable is positively skewed.
```





### 2. Attrition variable
```{r, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(df, aes(x = Attrition, y = prop.table(stat(count)),
               label = scales::percent(prop.table(stat(count))))) + 
  geom_bar(col = "blue", fill = "lightblue")+
  geom_text(stat = 'count', size = 5)+
  labs(y = "Frequency", title = "Barplot for Attrition") +
  theme_bw()
# In this data set 16% percent belongs to Attrition Yes group.
```

### 3. Monthly Income and Attrition
```{r, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(df, aes(x = Attrition, y = MonthlyIncome)) + 
  geom_boxplot(col = "blue", fill = "gold") + 
  labs(y = "Monthly Income (Salary)",x = "Attrition",
       title = "Boxplots of Monthly Income for Attrition groups") +
  theme_bw()

# According to the median values, employees who have lower salary tends to leave their current jobs.
```

### 4. Monthly Income and Age with Attrition
```{r, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(df, aes(x = Age, y = MonthlyIncome)) + 
  geom_point(col = "blue") + 
  geom_smooth(method='lm', formula= y~x, se = F, col = "red", size = 1) +
  labs(y = "Monthly Income (Salary)",x = "Age",
       title = "Scatter plot for Monthly Income vs Age for Attrition") +
  theme_bw() + 
  facet_wrap( ~ Attrition)

cor(df$Age, df$MonthlyIncome)
# There is a positive relationship between Monthly income and Age for both groups. When Age increases, Monthly income also increase. 

```

### 5. Monthly Income and Business Travel groups | Attrition and Business Travel groups
```{r, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(df, aes(x = BusinessTravel, fill = Attrition)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) + 
  labs(x = "Business Travel", y = "Attrition",
       title = "Business Travel with Attrition") + 
  theme_bw()

ggplot(df, aes(x = BusinessTravel, y = MonthlyIncome)) +
  geom_boxplot(fill = "gold") + 
  labs(x = "Business Travel", y = "Montly Income",
       title = "Montly Income for Business Travel groups") +
  theme_bw()

# Employees who are travel frequently have highest attrition rates and Non- travel group has lowest Income.
```

### 6. Hourly Rate, Daily Rate and Monthly Rate with Monthly Income and Attrition
```{r, message=FALSE, warning=FALSE, out.width="100%"}
p1 = ggplot(df, aes(x = HourlyRate, y = MonthlyIncome)) +
  geom_point(col = "blue") + 
  geom_smooth(method='lm', formula= y~x, se = F, col = "red", size = 1) +
  labs(x = "Hourly Rate", y = "Monthly Income", title = "Monthly Income vs Hourly Rate") +
  theme_bw() + 
  facet_wrap( ~ Attrition)

p2 = ggplot(df, aes(x = DailyRate, y = MonthlyIncome)) +
  geom_point(col = "blue") + 
  geom_smooth(method='lm', formula= y~x, se = F, col = "red", size = 1) +
  labs(x = "Daily Rate", y = "Monthly Income", title = "Monthly Income vs Daily Rate") +
  theme_bw() +
  facet_wrap( ~ Attrition)

p3 = ggplot(df, aes(x = MonthlyRate, y = MonthlyIncome)) +
  geom_point(col = "blue") + 
  geom_smooth(method='lm', formula= y~x, se = F, col = "red", size = 1) + 
  labs(x = "Monthly Rate", y = "Monthly Income", title = "Monthly Income vs Monthly Rate") +
  theme_bw() + 
  facet_wrap( ~ Attrition)

grid.arrange(p1,p2,p3)

round(cor(Attrition.Yes[c("HourlyRate","DailyRate","MonthlyRate","MonthlyIncome","DistanceFromHome","TotalWorkingYears","YearsInCurrentRole","YearsAtCompany","YearsWithCurrManager","YearsSinceLastPromotion")]),2)
round(cor(Attrition.No[c("HourlyRate","DailyRate","MonthlyRate","MonthlyIncome","DistanceFromHome","TotalWorkingYears","YearsInCurrentRole","YearsAtCompany","YearsWithCurrManager","YearsSinceLastPromotion")]),2)

# There is no relationship between following variables for both Attrition groups.
# 1. Hourly Rate and Monthly Income
# 2. Daily Rate and Monthly Income
# 3. Monthly Rate and Monthly Income

```


### 7. Monthly Income and Department | Attrition and Department
```{r, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(df, aes(x = Department, fill = Attrition)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) + 
  labs(x = "Department", y = "Attrition",
       title = "Department with Attrition") + 
  theme_bw()

ggplot(df, aes(x = Department, y = MonthlyIncome)) +
  geom_boxplot(fill = "gold") + 
  labs(x = "Department", y = "Montly Income",
       title = "Montly Income for Departments") +
  theme_bw()

# Higher attrition rate has sales department and HR department has lowest median for monthly income.
```

### 8. Distance from home with Monthly Income and Attrition
```{r, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(df, aes(x = DistanceFromHome, y = MonthlyIncome)) +
  geom_point(col = "blue") + 
  geom_smooth(method='lm', formula= y~x, se = F, col = "red", size = 1) +
  labs(x = "Distance From Home", y = "Monthly Income", 
       title = "Monthly Income vs Distance From Home") +
  theme_bw() + 
  facet_wrap( ~ Attrition)

cor(Attrition.Yes$DistanceFromHome, Attrition.Yes$MonthlyIncome)
cor(Attrition.No$DistanceFromHome, Attrition.No$MonthlyIncome)
```
# There is no relationship between Distance From Home and Monthly Income for both Attrition groups.



### 9.  Monthly Income and Education | Attrition and Education
```{r, message=FALSE, warning=FALSE, out.width="100%"}
df$Education = as.factor(df$Education)

ggplot(df, aes(x = Education, fill = Attrition)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) + 
  labs(x = "Education", y = "Attrition",
       title = "Education with Attrition") + 
  theme_bw()

ggplot(df, aes(x = Education, y = MonthlyIncome)) +
  geom_boxplot(fill = "gold") + 
  labs(x = "Education", y = "Montly Income",
       title = "Montly Income for Education") +
  theme_bw()

# Highest attrition rates has education level 1. 
# Highest median income has education level 5 group.

```


### 10. Monthly Income and Education Filed | Attrition and Education Filed
```{r, message=FALSE, warning=FALSE, out.width="100%"}

ggplot(df, aes(x = EducationField, fill = Attrition)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) + 
  labs(x = "Education Filed", y = "Attrition",
       title = "Education Filed with Attrition") + 
  theme_bw()

ggplot(df, aes(x = EducationField, y = MonthlyIncome)) +
  geom_boxplot(fill = "gold") + 
  labs(x = "Education Filed", y = "Montly Income",
       title = "Montly Income for Education Filed") +
  theme_bw()

# Highest attrition rates has Human Resource education field. 
# Highest median income has Marketing group.

```

### 11. Monthly Income and Environment Satisfaction | Attrition and Environment Satisfaction
```{r, message=FALSE, warning=FALSE, out.width="100%"}
df$EnvironmentSatisfaction = as.factor(df$EnvironmentSatisfaction)
ggplot(df, aes(x = EnvironmentSatisfaction, fill = Attrition)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) + 
  labs(x = "Environment Satisfaction", y = "Attrition",
       title = "Environment Satisfaction with Attrition") + 
  theme_bw()

ggplot(df, aes(x = EnvironmentSatisfaction, y = MonthlyIncome)) +
  geom_boxplot(fill = "gold") + 
  labs(x = "Environment Satisfaction", y = "Montly Income",
       title = "Montly Income for Environment Satisfaction") +
  theme_bw()

# Employees who are less satisfy about their environment has higher attrition rates. 
# Median incomes are very similar in all satisfaction levels.
```


### 12. Monthly Income and Gender | Attrition and Gender
```{r, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(df, aes(x = Gender, fill = Attrition)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) + 
  labs(x = "Gender", y = "Attrition",
       title = "Gender with Attrition") + 
  theme_bw()

ggplot(df, aes(x = Gender, y = MonthlyIncome)) +
  geom_boxplot(fill = "gold") + 
  labs(x = "Gender", y = "Montly Income",
       title = "Montly Income for Gender") +
  theme_bw()

# Both male and female group has similar attrition rates.
```

### 13. Monthly Income and Job Involvement | Attrition and Job Involvement

```{r, message=FALSE, warning=FALSE, out.width="100%"}
df$JobInvolvement = as.factor(df$JobInvolvement)

ggplot(df, aes(x = JobInvolvement, fill = Attrition)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) + 
  labs(x = "Job Involvement", y = "Attrition",
       title = "Job Involvement with Attrition") + 
  theme_bw()

ggplot(df, aes(x = JobInvolvement, y = MonthlyIncome)) +
  geom_boxplot(fill = "gold") + 
  labs(x = "Job Involvement", y = "Montly Income",
       title = "Montly Income for Job Involvement") +
  theme_bw()

# Employees with lower job involvement, have very higher attrition rate.
```


### 14. Monthly Income and Job Involvement | Attrition and Job Involvement
```{r, message=FALSE, warning=FALSE, out.width="100%"}
df$JobLevel = as.factor(df$JobLevel)

ggplot(df, aes(x = JobLevel, fill = Attrition)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) + 
  labs(x = "Job Level", y = "Attrition",
       title = "Job Level with Attrition") + 
  theme_bw()

ggplot(df, aes(x = JobLevel, y = MonthlyIncome)) +
  geom_boxplot(fill = "gold") + 
  labs(x = "Job Level", y = "Montly Income",
       title = "Montly Income for Job Level") +
  theme_bw()

# Employees who are in job level 1 have highest attrition rate.
# When job level increases, monthly income also increases.
```


### 15. Monthly Income and Job Role | Attrition and Job Role
```{r, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(df, aes(x = JobRole, fill = Attrition)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) + 
  labs(x = "Job Role", y = "Attrition",
       title = "Job Role with Attrition") + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust=1))

ggplot(df, aes(x = JobRole, y = MonthlyIncome)) +
  geom_boxplot(fill = "gold") + 
  labs(x = "Job Role", y = "Montly Income",
       title = "Montly Income for Job Role") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust=1))

# Sales representatives have higher attrition rate and lowest income.
# Managers abd Research directors have highest monthly income and lower attrition rate.

```


### 16. Monthly Income and Job Satisfaction | Attrition and Job Satisfaction
```{r, message=FALSE, warning=FALSE, out.width="100%"}
df$JobSatisfaction = as.factor(df$JobSatisfaction)

ggplot(df, aes(x = JobSatisfaction, fill = Attrition)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) + 
  labs(x = "Job Satisfaction", y = "Attrition",
       title = "Job Satisfaction with Attrition") + 
  theme_bw() 

ggplot(df, aes(x = JobSatisfaction, y = MonthlyIncome)) +
  geom_boxplot(fill = "gold") + 
  labs(x = "Job Satisfaction", y = "Montly Income",
       title = "Montly Income for Job Satisfaction") +
  theme_bw() 

# Employees who are less satisfy with their jobs have higher attrition rates.
```

### 17. Monthly Income and Marital Status | Attrition and Marital Status
```{r, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(df, aes(x = MaritalStatus, fill = Attrition)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) + 
  labs(x = "Marital Status", y = "Attrition",
       title = "Marital Status with Attrition") + 
  theme_bw() 

ggplot(df, aes(x = MaritalStatus, y = MonthlyIncome)) +
  geom_boxplot(fill = "gold") + 
  labs(x = "Marital Status", y = "Montly Income",
       title = "Montly Income for Marital Status") +
  theme_bw() 

# Single employees have highest attrition rates.
```

### 18. Monthly Income and Over Time | Attrition and Over Time
```{r, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(df, aes(x = OverTime, fill = Attrition)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) + 
  labs(x = "Over Time", y = "Attrition",
       title = "Over Time with Attrition") + 
  theme_bw() 

ggplot(df, aes(x = OverTime, y = MonthlyIncome)) +
  geom_boxplot(fill = "gold") + 
  labs(x = "Over Time", y = "Montly Income",
       title = "Montly Income for Over Time") +
  theme_bw() 

# Employees who work over time have higher attrition rate and lower monthly income.
```

### 19. Number of Companies Worked with Monthly Income and Attrition
```{r, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(df, aes(x = NumCompaniesWorked, y = MonthlyIncome)) +
  geom_point(col = "blue") + 
  geom_smooth(method='lm', formula= y~x, se = F, col = "red", size = 1) +
  labs(x = "Number of Companies Worked", y = "Monthly Income", 
       title = "Monthly Income vs Number of Companies Worked") +
  theme_bw() + 
  facet_wrap( ~ Attrition)

cor(Attrition.Yes$NumCompaniesWorked, Attrition.Yes$MonthlyIncome)
cor(Attrition.No$NumCompaniesWorked, Attrition.No$MonthlyIncome)

# There is a poor relationship between Monthly income and number of companies worked.
```


### 20. Percent Salary Hike with Monthly Income and Attrition
```{r, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(df, aes(x = PercentSalaryHike, y = MonthlyIncome)) +
  geom_point(col = "blue") + 
  geom_smooth(method='lm', formula= y~x, se = F, col = "red", size = 1) +
  labs(x = "Percent Salary Hike", y = "Monthly Income", 
       title = "Monthly Income vs Percent Salary Hike") +
  theme_bw() + 
  facet_wrap( ~ Attrition)

cor(Attrition.Yes$PercentSalaryHike, Attrition.Yes$MonthlyIncome)
cor(Attrition.No$PercentSalaryHike, Attrition.No$MonthlyIncome)

# It seems that Percent Salary Hike increases, monthly income decrease.
```

### 21. Monthly Income and Relationship Satisfaction | Attrition and Relationship Satisfaction
```{r, message=FALSE, warning=FALSE, out.width="100%"}
df$RelationshipSatisfaction = as.factor(df$RelationshipSatisfaction)

ggplot(df, aes(x = RelationshipSatisfaction, fill = Attrition)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) + 
  labs(x = "Relationship Satisfaction", y = "Attrition",
       title = "Relationship Satisfaction with Attrition") + 
  theme_bw() 

ggplot(df, aes(x = RelationshipSatisfaction, y = MonthlyIncome)) +
  geom_boxplot(fill = "gold") + 
  labs(x = "Relationship Satisfaction", y = "Montly Income",
       title = "Montly Income for Relationship Satisfaction") +
  theme_bw() 

# Employees who have low relationship satisfaction, have a higher attrition rate. But median incomes are similar in all levels.
```


### 22. Monthly Income and Stock Option Level | Attrition and Stock Option Level
```{r, message=FALSE, warning=FALSE, out.width="100%"}


df$StockOptionLevel = as.factor(df$StockOptionLevel)

ggplot(df, aes(x = StockOptionLevel, fill = Attrition)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) + 
  labs(x = "Stock Option Level", y = "Attrition",
       title = "Stock Option Level with Attrition") + 
  theme_bw() 

ggplot(df, aes(x = StockOptionLevel, y = MonthlyIncome)) +
  geom_boxplot(fill = "gold") + 
  labs(x = "Stock Option Level", y = "Montly Income",
       title = "Montly Income for Stock Option Level") +
  theme_bw() 

# Stock option levels 0 and 3 have higher attrition rates and lower median incomes.
```

### 23. Total Working Years with Monthly Income and Attrition
```{r, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(df, aes(x = TotalWorkingYears, y = MonthlyIncome)) +
  geom_point(col = "blue") + 
  geom_smooth(method='lm', formula= y~x, se = F, col = "red", size = 1) +
  labs(x = "Total Working Years", y = "Monthly Income", 
       title = "Monthly Income vs Total Working Years") +
  theme_bw() + 
  facet_wrap( ~ Attrition)

cor(Attrition.Yes$TotalWorkingYears, Attrition.Yes$MonthlyIncome)
cor(Attrition.No$TotalWorkingYears, Attrition.No$MonthlyIncome)

# There is strong positive relationship between Total Working Years and Monthly Income both attrition groups.
```

### 24. Training Times Last Year with Monthly Income and Attrition
```{r, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(df, aes(x = TrainingTimesLastYear, y = MonthlyIncome)) +
  geom_point(col = "blue") + 
  geom_smooth(method='lm', formula= y~x, se = F, col = "red", size = 1) +
  labs(x = "Training Times Last Year", y = "Monthly Income", 
       title = "Monthly Income vs Training Times Last Year") +
  theme_bw() + 
  facet_wrap( ~ Attrition)
```




### 25. Monthly Income and Work Life Balance | Attrition and Work Life Balance
```{r, message=FALSE, warning=FALSE, out.width="100%"}
df$WorkLifeBalance = as.factor(df$WorkLifeBalance)

ggplot(df, aes(x = WorkLifeBalance, fill = Attrition)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) + 
  labs(x = "Work Life Balance", y = "Attrition",
       title = "Work Life Balance with Attrition") + 
  theme_bw() 

ggplot(df, aes(x = WorkLifeBalance, y = MonthlyIncome)) +
  geom_boxplot(fill = "gold") + 
  labs(x = "Work Life Balance", y = "Montly Income",
       title = "Montly Income for Work Life Balance") +
  theme_bw() 

# Employees who have poor work life balance have higher attrition rate and lowest median income.
```

### 26. Years At Company with Monthly Income and Attrition
```{r, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(df, aes(x = YearsAtCompany, y = MonthlyIncome)) +
  geom_point(col = "blue") + 
  geom_smooth(method='lm', formula= y~x, se = F, col = "red", size = 1) +
  labs(x = "Years At Company", y = "Monthly Income", 
       title = "Monthly Income vs Years At Company") +
  theme_bw() + 
  facet_wrap( ~ Attrition)

cor(Attrition.Yes$YearsAtCompany, Attrition.Yes$MonthlyIncome)
cor(Attrition.No$YearsAtCompany, Attrition.No$MonthlyIncome)

# There is higher positive relationship between Years At Company and Monthly Income both attrition groups.
```


### 27. Years In Current Role with Monthly Income and Attrition
```{r, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(df, aes(x = YearsInCurrentRole, y = MonthlyIncome)) +
  geom_point(col = "blue") + 
  geom_smooth(method='lm', formula= y~x, se = F, col = "red", size = 1) +
  labs(x = "Years In Current Role", y = "Monthly Income", 
       title = "Monthly Income vs Years In Current Role") +
  theme_bw() + 
  facet_wrap( ~ Attrition)

cor(Attrition.Yes$YearsInCurrentRole, Attrition.Yes$MonthlyIncome)
cor(Attrition.No$YearsInCurrentRole, Attrition.No$MonthlyIncome)

# There is positive relationship between Years In Current Role and Monthly Income both attrition groups.
# Employees who work more than 15 years in current role, do not leave the company.
```


### 28. Years Since Last Promotion with Monthly Income and Attrition
```{r, message=FALSE, warning=FALSE, out.width="100%"}
ggplot(df, aes(x = YearsSinceLastPromotion, y = MonthlyIncome)) +
  geom_point(col = "blue") + 
  geom_smooth(method='lm', formula= y~x, se = F, col = "red", size = 1) +
  labs(x = "Years Since Last Promotion", y = "Monthly Income", 
       title = "Monthly Income vs Years Since Last Promotion") +
  theme_bw() + 
  facet_wrap( ~ Attrition)

cor(Attrition.Yes$YearsSinceLastPromotion, Attrition.Yes$MonthlyIncome)
cor(Attrition.No$YearsSinceLastPromotion, Attrition.No$MonthlyIncome)

# There is positive relationship between Years Since Last Promotion and Monthly Income both attrition groups.
```


### 29. Years With Current Manager with Monthly Income and Attrition
```{r, message=FALSE, warning=FALSE, out.width="100%"}

ggplot(df, aes(x = YearsWithCurrManager, y = MonthlyIncome)) +
  geom_point(col = "blue") + 
  geom_smooth(method='lm', formula= y~x, se = F, col = "red", size = 1) +
  labs(x = "Years With Current Manager", y = "Monthly Income", 
       title = "Monthly Income vs Years With Current Manager") +
  theme_bw() + 
  facet_wrap( ~ Attrition)

cor(Attrition.Yes$YearsWithCurrManager, Attrition.Yes$MonthlyIncome)
cor(Attrition.No$YearsWithCurrManager, Attrition.No$MonthlyIncome)

```

#---------evaluate the normality of variables----------

```{r, message=FALSE, warning=FALSE, out.width="100%"}

shapiro.test(df$MonthlyRate)
shapiro.test(df$PercentSalaryHike)
shapiro.test(df$MonthlyIncome)
shapiro.test(df$HourlyRate)
shapiro.test(df$YearsSinceLastPromotion)
shapiro.test(df$YearsWithCurrManager)
shapiro.test(df$YearsAtCompany)
shapiro.test(df$YearsInCurrentRole)
shapiro.test(df$TotalWorkingYears)
shapiro.test(df$NumCompaniesWorked)

```
#----------------------------------
# Man Whitney test to evaluate the difference between numeric variables in people with and without Attrition:

```{r, message=FALSE, warning=FALSE, out.width="100%"}

wilcox.test(NumCompaniesWorked ~ Attrition,data = df, alternative = "two.sided")
wilcox.test(MonthlyIncome ~ Attrition,data = df, alternative = "two.sided")
wilcox.test(PercentSalaryHike ~ Attrition,data = df, alternative = "two.sided")
wilcox.test(HourlyRate ~ Attrition,data = df, alternative = "two.sided")
wilcox.test(DistanceFromHome ~ Attrition,data = df, alternative = "two.sided")
wilcox.test(YearsSinceLastPromotion ~ Attrition,data = df, alternative = "two.sided")
wilcox.test(YearsWithCurrManager ~ Attrition,data = df, alternative = "two.sided")
wilcox.test(YearsAtCompany ~ Attrition,data = df, alternative = "two.sided")
wilcox.test(YearsInCurrentRole ~ Attrition,data = df, alternative = "two.sided")
wilcox.test(TotalWorkingYears ~ Attrition,data = df, alternative = "two.sided")
wilcox.test(MonthlyRate ~ Attrition,data = df, alternative = "two.sided")

#MonthlyIncome(p-value = 4.074e-09),DistanceFromHome(p-value = 0.02725),
#YearsWithCurrManager(p-value = 9.347e-07),YearsAtCompany(p-value = 3.11e-08),
#YearsInCurrentRole(p-value =9.482e-08),TotalWorkingYears(p-value = 4.042e-09) 
#were different with those with Attrition and those without Attrition


```

Evaluate the relationship between categorical variables with Attrition using chi chisquare test

```{r, message=FALSE, warning=FALSE, out.width="100%"}
chisq.test(df$JobSatisfaction,df$Attrition)
chisq.test(df$OverTime,df$Attrition)
chisq.test(df$JobInvolvement,df$Attrition)
chisq.test(df$StockOptionLevel,df$Attrition)
chisq.test(df$NumCompaniesWorked,df$Attrition)
chisq.test(df$WorkLifeBalance,df$Attrition)
chisq.test(df$TrainingTimesLastYear,df$Attrition)
chisq.test(df$PerformanceRating,df$Attrition)
chisq.test(df$RelationshipSatisfaction,df$Attrition)
chisq.test(df$EnvironmentSatisfaction,df$Attrition)
chisq.test(df$JobLevel,df$Attrition)
chisq.test(df$JobRole,df$Attrition)
chisq.test(df$Department,df$Attrition)
chisq.test(df$NumCompaniesWorked,df$Attrition)

#JobSatisfaction(p-value = 0.01115), OverTime(p-value = 2.333e-15),JobInvolvement(p-value = 5.211e-09),
# StockOptionLevel(p-value = 3.724e-12),WorkLifeBalance(p-value = 0.002495),df$EnvironmentSatisfaction(p-value = 0.01054) 
#Department(p-value = 0.009424),df$JobRole(p-value = 3.647e-10),NumCompaniesWorked(p-value = 0.01678)



```

##########################################
#### Evaluation the correlations with Monthly Income ####
##########################################


```{r, message=FALSE, warning=FALSE, out.width="100%"}
cor.test(df$Age, df$MonthlyIncome,
         method= "spearman",
         exact=FALSE,
         alternative="two.side")

#There is a positive correlation between age and income(R2=0.44,p-value < 2.2e-16)
```

```{r, message=FALSE, warning=FALSE, out.width="100%"}
cor.test(df$PercentSalaryHike, df$MonthlyIncome,
         method= "spearman",
         exact=FALSE,
         alternative="two.side")
#There is a weak correlation between PercentSalaryHike and income

```

```{r, message=FALSE, warning=FALSE, out.width="100%"}
cor.test(df$HourlyRate, df$MonthlyIncome,
         method= "spearman",
         exact=FALSE,
         alternative="two.side")
#There is a weak correlation between HourlyRate and income
```

```{r, message=FALSE, warning=FALSE, out.width="100%"}
cor.test(df$DistanceFromHome, df$MonthlyIncome,
         method= "spearman",
         exact=FALSE,
         alternative="two.side")
#There is a weak correlation between DistanceFromHome and income
```

```{r, message=FALSE, warning=FALSE, out.width="100%"}

cor.test(df$YearsSinceLastPromotion, df$MonthlyIncome,
         method= "spearman",
         exact=FALSE,
         alternative="two.side")
#There is a positive correlation between YearsSinceLastPromotion and income(R2=0.2683295,p-value = 8.191e-16)

```

```{r, message=FALSE, warning=FALSE, out.width="100%"}

cor.test(df$YearsWithCurrManager, df$MonthlyIncome,
         method= "spearman",
         exact=FALSE,
         alternative="two.side")
#There is a positive correlation between YearsWithCurrManager and income(R2=0.3644688, p-value < 2.2e-16)
```

```{r, message=FALSE, warning=FALSE, out.width="100%"}

cor.test(df$YearsAtCompany, df$MonthlyIncome,
         method= "spearman",
         exact=FALSE,
         alternative="two.side")

#There is a positive correlation between YearsAtCompany and income(R2=0.4595697 , p-value < 2.2e-16)

```

```{r, message=FALSE, warning=FALSE, out.width="100%"}

cor.test(df$YearsInCurrentRole, df$MonthlyIncome,
         method= "spearman",
         exact=FALSE,
         alternative="two.side")
#There is a positive correlation between YearsInCurrentRole and income(R2=0.4015205  , p-value < 2.2e-16)

```

```{r, message=FALSE, warning=FALSE, out.width="100%"}

cor.test(df$TotalWorkingYears, df$MonthlyIncome,
         method= "spearman",
         exact=FALSE,
         alternative="two.side")
#There is a strong positive correlation between TotalWorkingYears and income(R2=0.7158827   , p-value < 2.2e-16)
cor.test(df$MonthlyRate, df$MonthlyIncome,
         method= "spearman",
         exact=FALSE,
         alternative="two.side")
#-------------------------------

```


# Since MonthlyIncome variable is not normally distributed we use Kruskal-Wallis tests and Mann whitney U test for following analysis.

### 1. Monthly Income vs Attrition
```{r, message=FALSE, warning=FALSE, out.width="100%"}

wilcox.test(MonthlyIncome ~ Attrition,data = df, alternative = "two.sided")

#Monthlyincome  signifficantly different in people with or without Attrition d
#p-value = 4.074e-09


### 2. Monthly Income vs BusinessTravel
kruskal.test(MonthlyIncome ~ BusinessTravel,data = df)
kruskal.test(MonthlyIncome ~ NumCompaniesWorked,data = df)


### 3. Monthly Income vs Department
kruskal.test(MonthlyIncome ~ Department,data = df)
#Monthly income has a significant relationship with Department(p-value = 2.836e-06)


### 4. Monthly Income vs EducationField
kruskal.test(MonthlyIncome ~ EducationField,data = df)
#Monthly income has a significant relationship with EducationField(p-value = 0.008274)


### 5. Monthly Income vs Gender
wilcox.test(MonthlyIncome ~ Gender,data = df, alternative = "two.sided")
#p-value = 0.04623


### 6. Monthly Income vs JobRole
kruskal.test(MonthlyIncome ~ JobRole,data = df)
#p-value < 2.2e-16


### 7. Monthly Income vs MaritalStatus
kruskal.test(MonthlyIncome ~ MaritalStatus,data = df)
#p-value = 0.009288


### 8. Monthly Income vs OverTime
wilcox.test(MonthlyIncome ~ OverTime,data = df, alternative = "two.sided")

### 9. Monthly Income vs Education
kruskal.test(MonthlyIncome ~ Education,data = df)
#p-value = 0.0004072

### 10. Monthly Income vs EnvironmentSatisfaction
kruskal.test(MonthlyIncome ~ EnvironmentSatisfaction,data = df)

### 11. Monthly Income vs JobInvolvement
kruskal.test(MonthlyIncome ~ JobInvolvement,data = df)

### 12. Monthly Income vs JobLevel
kruskal.test(MonthlyIncome ~ JobLevel,data = df)
#p-value < 2.2e-16

### 13. Monthly Income vs JobSatisfaction
kruskal.test(MonthlyIncome ~ JobSatisfaction,data = df)

### 14. Monthly Income vs RelationshipSatisfaction
kruskal.test(MonthlyIncome ~ RelationshipSatisfaction,data = df)

### 15. Monthly Income vs StockOptionLevel
kruskal.test(MonthlyIncome ~ StockOptionLevel,data = df)
#p-value = 0.03185

### 16. Monthly Income vs WorkLifeBalance
kruskal.test(MonthlyIncome ~ WorkLifeBalance,data = df)


####17. Monthly Income vs NumCompaniesWorked
kruskal.test(MonthlyIncome ~ NumCompaniesWorked,data = df)
#p-value = 1.531e-08

# Median monthly incomes are not significantly differ in BusinessTravel, EnvironmentSatisfaction,
# OverTime,JobInvolvement,JobSatisfaction, RelationshipSatisfaction and WorkLifeBalance variables.


#Monthly income had a significant relationship with StockOptionLevel,JobLevel, Education,
#MaritalStatus, JobRole, Gender, EducationField, Department, Attrition,
#NumCompaniesWorked

```
# add some new variables to datasets increase the accuracy
```{r, message=FALSE, warning=FALSE, out.width="100%"}
df=df%>%
  mutate(year2=YearsInCurrentRole/YearsAtCompany)%>%
  mutate(year4=YearsInCurrentRole/TotalWorkingYears)%>%
  mutate(year5=df$YearsAtCompany/TotalWorkingYears)




cs2.NoAttrition=cs2.NoAttrition%>%
  mutate(year2=cs2.NoAttrition$YearsInCurrentRole/cs2.NoAttrition$YearsAtCompany)%>%
  mutate(year4=cs2.NoAttrition$YearsInCurrentRole/cs2.NoAttrition$TotalWorkingYears)%>%
  mutate(year5=cs2.NoAttrition$YearsAtCompany/cs2.NoAttrition$TotalWorkingYears)


cs2.NoSalary=cs2.NoSalary%>%
  mutate(year2=cs2.NoSalary$YearsInCurrentRole/cs2.NoSalary$YearsAtCompany)%>%
  mutate(year4=cs2.NoSalary$YearsInCurrentRole/cs2.NoSalary$TotalWorkingYears)%>%
  mutate(year5=cs2.NoSalary$YearsAtCompany/cs2.NoSalary$TotalWorkingYears)


df$year2=as.numeric(df$year2)
df$year4=as.numeric(df$year4)
df$year5=as.numeric(df$year5)

cs2.NoAttrition$year2=as.numeric(cs2.NoAttrition$year2)
cs2.NoAttrition$year4=as.numeric(cs2.NoAttrition$year4)
cs2.NoAttrition$year5=as.numeric(cs2.NoAttrition$year5)


cs2.NoSalary$year2=as.numeric(cs2.NoSalary$year2)
cs2.NoSalary$year4=as.numeric(cs2.NoSalary$year4)
cs2.NoSalary$year5=as.numeric(cs2.NoSalary$year5)
```

Dealing with missing data on in the new datasets

```{r, message=FALSE, warning=FALSE, out.width="100%"}

plot_missing(df)
sum(is.na(df))

for(i in 1:ncol(df))
{
  if(is.numeric(df[,i]))
  {
   df[is.na(df[,i]), i] <- median(df[,i], na.rm = TRUE)
  }
}
sum(is.na(df))


for(i in 1:ncol(cs2.NoAttrition))
{
  if(is.numeric(cs2.NoAttrition[,i]))
  {
    cs2.NoAttrition[is.na(cs2.NoAttrition[,i]), i] <- median(cs2.NoAttrition[,i], na.rm = TRUE)
  }
}
sum(is.na(cs2.NoAttrition))


for(i in 1:ncol(cs2.NoSalary))
{
  if(is.numeric(cs2.NoSalary[,i]))
  {
    cs2.NoSalary[is.na(cs2.NoSalary[,i]), i] <- median(cs2.NoSalary[,i], na.rm = TRUE)
  }
}
plot_missing(df)
sum(is.na(df))

```
 
 statistical analysis on the new variables:
```{r, message=FALSE, warning=FALSE, out.width="100%"}

wilcox.test(year2 ~ Attrition,data = df, alternative = "two.sided")
wilcox.test(year4 ~ Attrition,data = df, alternative = "two.sided")

cor.test(df$year5, df$MonthlyIncome,
         method= "spearman",
         exact=FALSE,
         alternative="two.side")
```


define the most important variables to determine attrition
```{r, message=FALSE, warning=FALSE, out.width="100%"}

library(xgboost)
tree <- rpart(Attrition ~ ., data = df)
# Fit an RF
set.seed(101) # for reproducibility
rfo <- randomForest(Attrition ~ ., data = df, importance = TRUE)
# Fit a GBM
set.seed(102) # for reproducibility

# Extract VI scores from each model
vi_tree <- tree$variable.importance
vi_rfo <- rfo$variable.importance # or use `randomForest::importance(rfo)`


# Load required packages
library(vip)
# Compute model-specific VI scores
vi(tree) # CART-like decision tree
vi(rfo) # RF


p1 <- vip(tree) + ggtitle("Single tree")

p2 <- vip(rfo) + ggtitle("Random forest")




# Display plots in a grid (Figure 1)
grid.arrange(p1, p2, p3, nrow = 1)
```


#Creat new datasets with the most important variables

```{r, message=FALSE, warning=FALSE, out.width="100%"}

df_attrition=df%>%
  select(OverTime
         ,JobSatisfaction,
         JobInvolvement,
         StockOptionLevel,
         WorkLifeBalance,
         EnvironmentSatisfaction,
         Department,
         JobRole,
         NumCompaniesWorked,
         MonthlyIncome,
         DistanceFromHome,
         YearsWithCurrManager,
         YearsAtCompany,
         YearsInCurrentRole,
         TotalWorkingYears,
         year2,
         year4
  )


cs2.NoAttrition=cs2.NoAttrition%>%select(
  OverTime,
  JobSatisfaction,
  JobInvolvement,
  StockOptionLevel,
  WorkLifeBalance,
  EnvironmentSatisfaction,
  Department,
  JobRole,
  NumCompaniesWorked,
  MonthlyIncome,
  DistanceFromHome,
  YearsWithCurrManager,
  YearsAtCompany,
  YearsInCurrentRole,
  TotalWorkingYears,
  year2,
  year4,
  
)


df_for_salary=df%>%
  select(Age, YearsSinceLastPromotion, YearsSinceLastPromotion,
         YearsWithCurrManager,
         year5,
         YearsAtCompany,
         YearsInCurrentRole,
         TotalWorkingYears,
         StockOptionLevel,
         JobLevel,
         Education,
         MaritalStatus,
         JobRole, 
         Gender, 
         EducationField,
         Department, 
         Attrition,
         NumCompaniesWorked)


cs2.NoSalary=cs2.NoSalary%>%
  select(Age, YearsSinceLastPromotion, YearsSinceLastPromotion,
         YearsWithCurrManager,
         year5,
         YearsAtCompany,
         YearsInCurrentRole,
         TotalWorkingYears,
         StockOptionLevel,
         JobLevel,
         Education,
         MaritalStatus,
         JobRole, 
         Gender, 
         EducationField,
         Department, 
         Attrition,
         NumCompaniesWorked
  )
```


#Converting factor variables to numeric variables(dummies)
```{r, message=FALSE, warning=FALSE, out.width="100%"}

dmy <- dummyVars(" ~ .", data = df_attrition)
df_attrition1 <- data.frame(predict(dmy, newdata = df_attrition))



dmy1=dummyVars(" ~ .", data = cs2.NoAttrition)
cs2.NoAttrition_test<- data.frame(predict(dmy1, newdata = cs2.NoAttrition))

dmy2<- dummyVars(" ~ .", data = df_for_salary)
df_for_salary1 <- data.frame(predict(dmy2, newdata = df_for_salary))


cs2.NoSalary$StockOptionLevel=as.factor(cs2.NoSalary$StockOptionLevel)
dmy3=dummyVars(" ~ .", data = cs2.NoSalary)
cs2.NoSalary_test<- data.frame(predict(dmy3, newdata = cs2.NoSalary))


df_attrition2=cbind(df_attrition1,new_col=df["Attrition"])

df_for_salary2=cbind(df_for_salary1,new_col=df["MonthlyIncome"])

```




#Normalizing the numeric variables
```{r, message=FALSE, warning=FALSE, out.width="100%"}

library(tidyverse)

normalize=function(x){
  return((x-min(x))/(max(x)-min(x)))
}

df_attrition2=df_attrition2%>%
  mutate(DistanceFromHome=normalize(DistanceFromHome))%>%
  mutate(YearsWithCurrManager=normalize(YearsWithCurrManager))%>%
  mutate(YearsAtCompany=normalize(YearsAtCompany))%>%
  mutate(TotalWorkingYears=normalize(TotalWorkingYears))%>%
  mutate(YearsInCurrentRole=normalize(YearsInCurrentRole))%>%
  mutate(MonthlyIncome=normalize(MonthlyIncome))

cs2.NoAttrition_test= cs2.NoAttrition_test%>%
  mutate(DistanceFromHome=normalize(DistanceFromHome))%>%
  mutate(YearsWithCurrManager=normalize(YearsWithCurrManager))%>%
  mutate(YearsAtCompany=normalize(YearsAtCompany))%>%
  mutate(TotalWorkingYears=normalize(TotalWorkingYears))%>%
  mutate(YearsInCurrentRole=normalize(YearsInCurrentRole))%>%
  mutate(MonthlyIncome=normalize(MonthlyIncome))


df_for_salary2=df_for_salary2%>%
  mutate(Age=normalize(Age))%>%
  mutate(YearsWithCurrManager=normalize(YearsWithCurrManager))%>%
  mutate(YearsSinceLastPromotion=normalize(YearsSinceLastPromotion))%>%
  mutate(YearsAtCompany=normalize(YearsAtCompany))%>%
  mutate(year5=normalize(year5))%>%
  mutate(TotalWorkingYears=normalize(TotalWorkingYears))


cs2.NoSalary_test= cs2.NoSalary_test%>%
  mutate(Age=normalize(Age))%>%
  mutate(YearsWithCurrManager=normalize(YearsWithCurrManager))%>%
  mutate(YearsSinceLastPromotion=normalize(YearsSinceLastPromotion))%>%
  mutate(YearsAtCompany=normalize(YearsAtCompany))%>%
  mutate(year5=normalize(year5))%>%
  mutate(TotalWorkingYears=normalize(TotalWorkingYears))
```


#Dealing with the missing data
```{r, message=FALSE, warning=FALSE, out.width="100%"}


plot_missing(df)
sum(is.na(df))

for(i in 1:ncol(df))
{
  if(is.numeric(df[,i]))
  {
    df[is.na(df[,i]), i] <- median(df[,i], na.rm = TRUE)
  }
}
sum(is.na(df))


for(i in 1:ncol(cs2.NoAttrition))
{
  if(is.numeric(cs2.NoAttrition[,i]))
  {
    cs2.NoAttrition[is.na(cs2.NoAttrition[,i]), i] <- median(cs2.NoAttrition[,i], na.rm = TRUE)
  }
}
sum(is.na(cs2.NoAttrition))


for(i in 1:ncol(cs2.NoSalary))
{
  if(is.numeric(cs2.NoSalary[,i]))
  {
    cs2.NoSalary[is.na(cs2.NoSalary[,i]), i] <- median(cs2.NoSalary[,i], na.rm = TRUE)
  }
}
plot_missing(df)
sum(is.na(df))
```


#Using naive bayes to predict attrition

```{r, message=FALSE, warning=FALSE, out.width="100%"}

set.seed(1234)
sample_set=sample(nrow(df_attrition2),round(nrow(df_attrition2)*0.75),replace=FALSE)
df_attrition2_train=df_attrition2[sample_set,]
df_attrition2_test=df_attrition2[-sample_set,]
naive =  naiveBayes(Attrition ~ ., data = df_attrition2_train)

pred =predict(naive,df_attrition2_test,type="class")
 
pred_table=table(df_attrition2_test$Attrition,pred)
pred_table
```

```{r, message=FALSE, warning=FALSE, out.width="100%"}

sum(diag(pred_table))/nrow(df_attrition2_test)
tab.naive = table(predicted = pred,Actual =  df_attrition2_test$Attrition)
(sensitivity = round(tab.naive[2,2]*100/(tab.naive[2,2] + tab.naive[1,2])))
(specificity = round(tab.naive[1,1]*100/(tab.naive[1,1] + tab.naive[2,1])))


```



```{r, message=FALSE, warning=FALSE, out.width="100%"}

final.cls.model = naiveBayes(Attrition ~ ., data = df_attrition2)
pred4 = predict(final.cls.model, newdata = df_attrition2)

tab.naive = table(predicted = pred4,Actual =  df_attrition2$Attrition)
(sensitivity = round(tab.naive[2,2]*100/(tab.naive[2,2] + tab.naive[1,2])))
(specificity = round(tab.naive[1,1]*100/(tab.naive[1,1] + tab.naive[2,1])))
attrition_matrix=confusionMatrix(pred4,df_attrition2$Attrition,positive= "Yes")
attrition_matrix
precision=posPredValue(pred4,df_attrition2$Attrition,positive= "Yes") 
precision
sensitivity=sensitivity(pred4,df_attrition2$Attrition,positive= "Yes")
sensitivity
specificity=specificity(pred,df_attrition2$Attrition,negative= "No")
specificity
f1_score=(2*precision*sensitivity)/(precision+sensitivity)
f1_score
predfinal=predict(final.cls.model,newdata=cs2.NoAttrition_test)
predfinal
cs2.NoAttrition =  read.csv("/Users/owner/Desktop/homework/unit14,15(case sudy)/Unit%2014%20and%2015%20Case%20Study%202 2/CaseStudy02/CaseStudy2CompSet No Attrition.csv",stringsAsFactors = TRUE)
pred.df = data.frame(ID = cs2.NoAttrition$ID, Attrition = predfinal)
```
#---------------------------------
# Variable Importance based on naiive bayes model
```{r, message=FALSE, warning=FALSE, out.width="100%"}

Grid = data.frame(usekernel=TRUE,laplace = 0,adjust=1)
mdl = train(Attrition ~ .,data=df_attrition2,method="naive_bayes",
            trControl=trainControl(method="none"),
            tuneGrid=Grid)
varImp(mdl)
```

```{r, message=FALSE, warning=FALSE, out.width="100%"}

for(i in 1:ncol(df))
{
  if(is.numeric(df[,i]))
  {
    df[is.na(df[,i]), i] <- median(df[,i], na.rm = TRUE)
  }
}
sum(is.na(df))


for(i in 1:ncol(cs2.NoAttrition))
{
  if(is.numeric(cs2.NoAttrition[,i]))
  {
    cs2.NoAttrition[is.na(cs2.NoAttrition[,i]), i] <- median(cs2.NoAttrition[,i], na.rm = TRUE)
  }
}
sum(is.na(cs2.NoAttrition))


for(i in 1:ncol(cs2.NoSalary))
{
  if(is.numeric(cs2.NoSalary[,i]))
  {
    cs2.NoSalary[is.na(cs2.NoSalary[,i]), i] <- median(cs2.NoSalary[,i], na.rm = TRUE)
  }
}
plot_missing(df)
sum(is.na(df))

sum(is.na(cs2.NoAttrition))


for(i in 1:ncol(df_attrition2))
{
  if(is.numeric(df_attrition2[,i]))
  {
    df_attrition2[is.na(df_attrition2[,i]), i] <- median(df_attrition2[,i], na.rm = TRUE)
  }
}
sum(is.na(df_attrition2))
```

#Use of GBM model to predict attrition
### GBM ###
```{r, message=FALSE, warning=FALSE, out.width="100%"}

library(gbm)
df_attrition2$Attrition = ifelse(df_attrition2$Attrition == "Yes",1,0)
gbm.mod_final = gbm(formula = Attrition ~ ., data = df_attrition2,interaction.depth = 3,
                    distribution = "bernoulli", n.trees = 5000,shrinkage = 0.1,
                    n.minobsinnode = 10,cv.folds = 10)
pred10 = predict(gbm.mod_final, newdata = df_attrition2,type = "response")
pred10 = ifelse(pred10 > 0.5,1,0)
tab.gbm = table(predicted = pred10,Actual =  df_attrition2$Attrition)
(sensitivity = round(tab.gbm[2,2]*100/(tab.gbm[2,2] + tab.gbm[1,2])))
(specificity = round(tab.gbm[1,1]*100/(tab.gbm[1,1] + tab.gbm[2,1])))

```
#GBM had a sensitivity of 99% , however the speficiy was not high


#Use of KNN for prediction od attrition

#-------------------KNN----------------------
```{r, message=FALSE, warning=FALSE, out.width="100%"}

library(class)
idx = sample.int(n = nrow(df_attrition2), size = floor(0.75*nrow(df_attrition2)), replace = F)
train = df_attrition2[idx,]


test = df_attrition2[-idx,]
trn_target = train$Attrition
trn = train[,-44]
tst_target = test$Attrition
tst = test[,-44]

pred = knn(train = trn, test = tst, cl = trn_target, k = 6)
model_table=table(tst_target,pred)
model_table
sum(diag(model_table))/nrow(tst)


Accuracy = NULL
mis = NULL
sen = NULL
spe = NULL

for(i in 1:50)
{
  pred = knn(train = trn, test = tst, cl = trn_target, k = i)
  head(pred)
  model_table=table(trn_target)
  tab = table(Predicted = pred, Real = tst_target)
  Accuracy[i] = ((tab[1,1] + tab[2,2])/sum(tab))*100
  mis[i] = round((tab[1,2]+tab[2,1])/sum(tab),2)
  sen[i] = round(tab[2,2]/(tab[2,2]+tab[1,2]),2)
  spe[i] = round(tab[1,1]/(tab[1,1]+tab[2,1]),2)
}
plot(x = c(1:50), y = Accuracy, xlab = "k", pch = 19, type = "b")
abline(v = which.max(Accuracy), col = "red", lwd = 2)

data.frame(Measure = c("Accuracy","Misclassification Rate","Sensitivity","Specificity"),
           Value = c(round(Accuracy[6],2),round(mis[6],2),round(sen[6],2),round(spe[6],2)))


Attrition=cs2.NoAttrition_test$Attrition
```
#-----------------------------------



```{r, message=FALSE, warning=FALSE, out.width="100%"}
for(i in 1:ncol(cs2.NoSalary))
{
  if(is.numeric(cs2.NoSalary[,i]))
  {
    cs2.NoSalary[is.na(cs2.NoSalary[,i]), i] <- median(cs2.NoSalary[,i], na.rm = TRUE)
  }
}
```

```{r, message=FALSE, warning=FALSE, out.width="100%"}

set.seed(2021) 
train_ind = sample(seq_len(nrow(df_for_salary2)), size = floor(0.7 * nrow(df_for_salary2)))
train = df_for_salary2[train_ind, ]
test = df_for_salary2[-train_ind, ]

model2 = lm(MonthlyIncome ~ ., data = train)
summary(model2)
pred1 = predict(model2, newdata = test)
(RMSE.test = sqrt(mean((pred1 - test$MonthlyIncome)^2)))
```

```{r, message=FALSE, warning=FALSE, out.width="100%"}

final.reg.model = lm(MonthlyIncome ~ ., data = df_for_salary2)
summary(final.reg.model)
pred1 = predict(final.reg.model, newdata = df_for_salary2)
(RMSE.tr.reg = sqrt(mean((pred1 - df_for_salary2$MonthlyIncome)^2)))
```


lets do some data preprocessing
```{r, message=FALSE, warning=FALSE, out.width="100%"}

cs2.NoSalary$StockOptionLevel=as.factor(cs2.NoSalary$StockOptionLevel)
cs2.NoSalary_test$MonthlyIncome=NaN
```


lets do some data preprocessing
```{r, message=FALSE, warning=FALSE, out.width="100%"}


names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "MaritalStatus.Divorced"] <- "MaritalStatusDivorced"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "MaritalStatus.Married"] <- "MaritalStatusMarried"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "MaritalStatus.Single"] <- "MaritalStatusSingle"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "Gender.Female"] <- "GenderFemale"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "Gender.Male"] <- "GenderMale"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Human.Resources"] <- "EducationFieldHuman.Resources"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Life.Sciences"] <- "EducationFieldLife.Sciences"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Marketing"] <- "EducationFieldMarketing"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Medical"] <- "EducationFieldMedical"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Other"] <- "EducationFieldOther"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Technical.Degree"] <- "EducationFieldTechnical.Degree"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "Department.Human.Resources"] <- "DepartmentHuman.Resources"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "Department.Research...Development"] <- "DepartmentResearch...Development"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "Department.Human.Resources"] <- "DepartmentHuman.Resources"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "Department.Research...Development"] <- "DepartmentResearch...Development"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "Department.Sales"] <- "DepartmentSales"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Human.Resources"] <- "EducationFieldHuman.Resources"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Life.Sciences"] <- "EducationFieldLife.Sciences"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Human.Resources"] <- "EducationFieldHuman.Resources"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Marketing"] <- "EducationFieldMarketing"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Medical"] <- "EducationFieldMedical"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Other"] <- "EducationFieldOther"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Technical.Degree"] <- "EducationFieldTechnical.Degree"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "Gender.Female"] <- "GenderFemale"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "Gender.Male"] <- "GenderMale"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "MaritalStatus.Divorced"] <- "MaritalStatusDivorced"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "MaritalStatus.Married"] <- "MaritalStatusMarried"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "MaritalStatus.Single"] <- "MaritalStatusSingle"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "OverTime.No"] <- "OverTimeNo"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "OverTime.Yes"] <- "OverTimeYes"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "MaritalStatus.Divorced"] <- "MaritalStatusDivorced"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "MaritalStatus.Married"] <- "MaritalStatusMarried"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "Department.Human.Resources"] <- "DepartmentHuman.Resources"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "Department.Research...Development"] <- "DepartmentResearch...Development"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "Department.Sales"] <- "DepartmentSales"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Human.Resources"] <- "EducationFieldHuman.Resources"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Life.Sciences"] <- "EducationFieldLife.Sciences"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Human.Resources"] <- "EducationFieldHuman.Resources"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Marketing"] <- "EducationFieldMarketing"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Medical"] <- "EducationFieldMedical"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Other"] <- "EducationFieldOther"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Technical.Degree"] <- "EducationFieldTechnical.Degree"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "Gender.Female"] <- "GenderFemale"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "Gender.Male"] <- "GenderMale"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "MaritalStatus.Divorced"] <- "MaritalStatusDivorced"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "MaritalStatus.Married"] <- "MaritalStatusMarried"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "MaritalStatus.Single"] <- "MaritalStatusSingle"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "OverTime.No"] <- "OverTimeNo"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "OverTime.Yes"] <- "OverTimeYes"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "Department.Human.Resources"] <- "DepartmentHuman.Resources"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "Department.Research...Development"] <- "DepartmentResearch...Development"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "Department.Sales"] <- "DepartmentSales"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Human.Resources"] <- "EducationFieldHuman.Resources"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Life.Sciences"] <- "EducationFieldLife.Sciences"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Human.Resources"] <- "EducationFieldHuman.Resources"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Marketing"] <- "EducationFieldMarketing"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Medical"] <- "EducationFieldMedical"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Other"] <- "EducationFieldOther"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "EducationField.Technical.Degree"] <- "EducationFieldTechnical.Degree"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "Gender.Female"] <- "GenderFemale"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "Gender.Male"] <- "GenderMale"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "MaritalStatus.Divorced"] <- "MaritalStatusDivorced"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "MaritalStatus.Married"] <- "MaritalStatusMarried"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "MaritalStatus.Single"] <- "MaritalStatusSingle"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "OverTime.No"] <- "OverTimeNo"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "OverTime.Yes"] <- "OverTimeYes"
names(cs2.NoSalary_test)[names(cs2.NoSalary_test) == "OverTime.Yes"] <- "OverTimeYes"

```

```{r, message=FALSE, warning=FALSE, out.width="100%"}

cs2.NoSalary1 = read.csv("/Users/owner/Desktop/homework/unit14,15(case sudy)/Unit%2014%20and%2015%20Case%20Study%202 2/CaseStudy02/CaseStudy2CompSet No Salary.csv",stringsAsFactors = TRUE)
pred2 = predict(final.reg.model, newdata = cs2.NoSalary_test)

pred.df = data.frame(ID = cs2.NoSalary1$ID, MonthlyIncome = pred2)
```



